A Dynamic Intrafamily Model of Child Behavior Problems and Birth Timing

### 2019-02-21 inst/paper/paper.Rmd
Removing under development syntax
Migrating things under development into inst so paper compiles correctly.

# library(birthtiming) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

@@

```{r resultsdata, include=FALSE}
# child_difficulty <- load_and_format_NLSY()
# naive_tidy <- run_naive_sem()
load("../data/derived_data/naive_tidy.RData")
load("../data/derived_data/child_difficulty.RData")
```

>>>>

# birthtiming package currently disabled while in redevelopment
# library(birthtiming) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

@@

```{r resultsdata, include=FALSE}
child_difficulty <- gen_birthtiming_data(min_children=2, max_children=10) %>%
                                        filter(!is.na(difficulty_1) & !is.na(difficulty_2)) 
naive_tidy <- run_naive_sem()
load("../data/derived_data/naive_tidy.RData")
load("../data/derived_data/child_difficulty.RData")
```
